Scalar Items in Embedded Position: {A}n Experimental Revisit

### 2012-06-28 text/paper/paper.tex
K2 paper sec com
paper sec com

\documentclass[fleqn,reqno,10pt]{article}

\usepackage{myarticlestyledefault}

\usepackage{mypackages}
\usepackage{mycommands}
\usepackage{myenvironments}

\usepackage[]{svninfo}

@@

\newcommand{\lc}{\acro{lc}}
\newcommand{\ec}{\acro{ec}}

\DefineNamedColor{named}{mycol}{cmyk}{0.6,0.6,0,0}
\DefineNamedColor{named}{mygray}{cmyk}{0.05,0.05,0.05,0.05}
\DefineNamedColor{named}{mygraylight}{cmyk}{0.017,0.017,0.017,0.017}

\newcommand{\mymark}[1]{{\color{mycol}{#1}}}

\title{Scalar Items in Embedded Position: {A}nother Experimental Approach}
\author{Fabian Schlotterbeck, Michael Franke and Petra Augurzky}
\date{}

@@

@@

This paper deals with the interpretation of two types of
sentences, namely:

\begin{exe}
\ex \label{bsp:AE}
  \mymark{All} of the students read \mymark{some} of the
  papers. \hfill (\AE)
\ex \label{bsp:GE} 
  \mymark{Exactly one} of the students read \mymark{some} of the
  papers. \hfill (\GE)
\end{exe}

\noindent In \as-sentences a scalar item \emph{some} takes scope under
a universal quantifier \emph{all}. In \es-sentences a scalar item
\emph{some} takes scope under a non-monotonic quantifier \emph{exactly
  one}. Scalar \emph{some} is usually assumed to receive a semantic
interpretation similar to logical $\exists$, so that the sentence
\emph{Some boys cried} is literally true in a situation where all
boys cried. But it is also known to invite upper-bounding inferences
in plain utterances:

\begin{exe}
  \ex \label{bsp:Plain-SI}
    \begin{xlist}
      \ex \label{bsp:Plain-SI-Target} Hans solved some of the problems.
      \ex \label{bsp:Plain-SI-Implicature} $\implicates$ Hans solved some but not all of the problems.
    \end{xlist}
\end{exe}

\noindent The classical explanation of this inference, following the
pioneering work of \citet{Grice1975:Logic-and-Conve}, has it that
(\ref{bsp:Plain-SI-Implicature}) is a pragmatic inference, a so-called
\emph{quantity implicature}, derived by an abductive inference as the
best explanation of why am informed, knowledgable and cooperative
speaker has uttered (\ref{bsp:Plain-SI-Target}) when she could also
have uttered the semantically stronger and relevant:\dn{redo labels of
  examples}

\begin{exe}
  \exr{bsp:Plain-SI}
    \begin{xlist}
      \exi{c.} \label{bsp:Plain-SI-Alternative} Hans solved all of the problems.
    \end{xlist}
\end{exe}

\noindent If this upper-bounding inference would occur often and
systematically enough, then it may well be that also embedded
occurrences of \emph{some} get enriched, in some fashion or other, to
contribute the enriched meaning \emph{some but not all} also under the
scope of other logical operators. Indeed, even
\citeauthor{Grice1975:Logic-and-Conve} envisaged this possibility when
he wrote: ``It may not be impossible for what starts life, so to
speak, as a conversational implicature to become conventionalized''
\citep[p.58]{Grice1975:Logic-and-Conve}. But then there are at least
three relevant candidate readings for \as- and \es-sentences: (i) a
\emph{literal reading} like in (\ref{bsp:AE-Literal}) and
(\ref{bsp:GE-Literal}) where \emph{some} has only its literal meaning;
(ii) a \emph{global reading} like in (\ref{bsp:AE-Global}) and
(\ref{bsp:GE-Global}) where, according to the Gricean intuition, we
enrich utterances of (\ref{bsp:AE}) and (\ref{bsp:GE}) with the
negation of alternativ utterances of the corresponding sentences
(\ref{bsp:AE-Alternative}) and (\ref{bsp:GE-Alternative}) where
\emph{some} is replaced by \emph{all}; and also (iii) a \emph{local
  reading} like in (\ref{bsp:AE-Local}) and (\ref{bsp:GE-Local}) where
\emph{some} is read to mean \emph{some but not all} in the scope of
the embedding quantifier.

% DIRTY!!!
\setcounter{exx}{0}

\begin{exe}

@@

  \begin{xlist}
  \ex \label{bsp:AE-Literal} \mymark{All} of the students read
    {\mymark{some and maybe all}} of the papers. \hfill (\as-\lit)
  \ex \label{bsp:AE-Global}
    \mymark{All} of the students read \mymark{some} 
    and  \hfill (\as-\glb)\\
    \mymark{not all} of the students read \mymark{all} of the papers.
  \ex \label{bsp:AE-Local}
    \mymark{All} of the students read {\mymark{some  but not all}} of the
    papers. \hfill (\as-\loc)
  \end{xlist}

\ex \mymark{Exactly one} of the students read {\mymark{some}} of the
  papers.

  \begin{xlist}
  \ex \label{bsp:GE-Literal} \mymark{Exactly one} of the students read
    {\mymark{some and maybe all}} of the papers. \hfill (\es-\lit)
  \ex \label{bsp:GE-Global}
    \mymark{Exactly one} of the students read \mymark{some} 
    and  \hfill (\es-\glb)\\
    \mymark{not all} of the students read \mymark{all} of the papers.
  \ex \label{bsp:GE-Local}
    \mymark{Exactly one} of the students read {\mymark{some  but not all}} of the
    papers. \hfill (\es-\loc)
  \end{xlist}

\ex \label{bsp:AE-Alternative} \mymark{All} of the students read
  {\mymark{all}} of the papers.

\ex \label{bsp:GE-Alternative} \mymark{Exactly one} of the students
  read {\mymark{all}} of the papers.

\end{exe}

\noindent Section~\ref{sec:get-know-your} will discuss these reading
in more detail and, by giving some helpful illustrations, make clear
that these readings are all distinct but logically dependent
on each other in interesting ways.

The main question we are interested in here is which of these three
conceivable readings is available to subjects na\"{i}ve to all
pragmatic theory. We are moreover interested in the more refined
question which of the available readings na\"{i}ve subjects prefer.

Addressing these issues empirically is highly relevant because they
lie at the heart of the current debate of the exact location and
nature of the interface between semantics and pragmatics. There are
three major camps which are ---more or less fiercely--- involved in
this border war, all of which make different predictions about
availability and preferences of readings. We will give a more detailed
description of the various theoretical positions below in
Section~\ref{sec:theories-predictions}, but on a first rough
approximation the situation is the following. Firstly, there are
\mymark{pragmatic traditionalists} who seek to conserve the spirit of
\citeauthor{Grice1975:Logic-and-Conve}'s
(\citeyear{Grice1975:Logic-and-Conve}) original ideas as much as
possible
\citep[e.g.][]{Spector2006:Scalar-Implicat,Sauerland2004:Scalar-Implicat,Russell2006:Against-Grammat,vanRooijSchulz:ExhaustiveInterpretation,Geurts2010:Quantity-Implic,Franke2011:Quantity-Implic}. Traditionalists
happily acknowledge the existence of global readings, but might
consider local readings either unavailable or a beast distinct from
scalar implicatures. Opposed to that is the camp of \mymark{lexical
  conventionalists}
\citep[e.g.][]{LevinsonPresumptiveMeanings2000,Chierchia:2004_ScalarImplicatures}
who maintain that scalar \emph{some} is lexically ambiguous between
the standard logical meaning \emph{some and maybe all} and the
upper-bounded meaning \emph{some but not all}. As the latter is
considered a default, lexical conventionalism has no problem
accounting for local readings, and in fact would consider these the
preferred readings. Thirdly and finally, there is the camp of
\mymark{grammaticalists} who defend that the distribution of
upper-bounded readings of \emph{some} is best explained by postulating
a silent operator, akin to the meaning of the particle \emph{only}
\citep{Chierchia2006:Broaden-Your-Vi,Fox2007:Free-Choice-and,ChierchiaFox2008:The-Grammatical,Chierchia2012:FC-Nominals-and,Sauerland2012:The-Computation}. According
to the grammatical view, this silent operator may be applied in
compositional semantics also in the scope of other logical operators,
but the availability of readings is constraint by the \emph{strongest
  meaning hypothesis}
\citep{DalrympleKanazawa1998:Reciprocal-Expr}. Details follow in
Section~\ref{sec:theories-predictions}, but suffice it to just state
already that grammaticalist theories predict that all three types of
readings are available. Moreover, according to the grammatical view,
the local reading is preferred for \as-sentences, while the global one
is preferred for \es-sentences. (More precisely, but see
Section~\ref{sec:theories-predictions}, depending on the variant of
the strongest meaning hypothesis employed, either the global reading
is predicted to be preferred for \es-sentences, or the global and the
local reading are predicted to be equally preferred.)

\bigskip

>>>>

\documentclass[fleqn,reqno,10pt,draft]{article}

\usepackage[natbib=true,
            style=authoryear-comp,
            backend=bibtex,
            sortcites=false,
            maxnames=2,
            doi=false,
            url=false]{biblatex}
% \bibliography{../helpers/MyRefGlobal}
\bibliography{paper}

\usepackage[final,            % override "draft" which means "no nothing"
            colorlinks,       % rather than outlining them in boxes
            linkcolor=gray,   % override truly awful colour choices
            citecolor=gray,   %   (ditto)
            urlcolor=gray,    %   (ditto)
            plainpages=false, % to overcome complaints with multiple
            pdfpagelabels,    % multiple page 1-s due to preface
            hypertexnames=false % solves warning, but interferes with
                                % index and \autoref apparently
            ]{hyperref}

\usepackage{amsmath}            % Formeln
\usepackage{amsfonts}           % Fonts for Formulas
\usepackage{amssymb}
\usepackage[final]{graphicx}
\usepackage{booktabs}
\usepackage{enumerate}
\usepackage{lipsum}
\usepackage{txfonts} % for strict implication symbols
\usepackage{soul}
\usepackage{relsize} % provides command \relsize{+/-x} for relative
                     % font size changes
\usepackage[german,english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc} 
\usepackage{subfig}
\usepackage{xypic}
\usepackage{url}
\usepackage{tikz}
\usetikzlibrary{arrows,shapes,automata,backgrounds,petri,fit,decorations.pathmorphing}
\usepackage{refcount}
\usepackage{xspace} % for \xspace in definition of acronyms etc.
\usepackage{attrib} % for right-aligned references at the end of
                    % quotes; part of Frankenstein bundle, but 
\renewcommand\PreTrib {}   % overwrite these commands, from attrib.sty
\renewcommand\PostTrib {}  % to suppress additional brackets around
                           % attributions

\usepackage{pgfplots}

\usepackage{../helpers/gb4e_micha}
\usepackage{../helpers/proofing}

\usepackage{../helpers/mycommands}
% \usepackage{../helpers/myenvironments}

\usepackage[]{svninfo}
\usepackage{subfig}

%%%% Additional Macros

@@

\newcommand{\lc}{\acro{lc}}
\newcommand{\ec}{\acro{ec}}
\newcommand{\LC}{\lc}
\newcommand{\EC}{\ec}

\newcommand{\exh}{\ensuremath{\mathrm{Exh}}}
\newcommand{\alt}{\ensuremath{\mathrm{Alt}}}

%%%% Document

\title{Scalar Items in Embedded Position: {A}n Experimental Revisit}
\author{Fabian Schlotterbeck, Michael Franke and Petra Augurzky}
\date{}

@@

\tableofcontents

@@

The existential quantifier \emph{some} is usually assumed to receive a
semantic interpretation similar to logical $\exists$, so that the
sentence \emph{Some boys cried} is literally true in a situation where
all boys cried. But it is also usually considered to be a
\mymark{scalar item} in that its use invites comparison with (at
least) the semantically stronger universal quantifier \emph{all}
\citep[c.f.][]{Horn1972:On-the-Semantic,Gazdar1979:Pragmatics:-Imp,AtlasLevinson1981}. This
comparison can lead to an upper-bounding meaning enrichment, e.g.,
when an utterance of (\ref{bsp:Plain-SI-Target}) is taken to invite
the inference in (\ref{bsp:Plain-SI-Implicature}).

\begin{exe}
  \ex \label{bsp:Plain-SI}
    \begin{xlist}
      \ex \label{bsp:Plain-SI-Target} Hans solved some of the
        problems.
      \ex \label{bsp:Plain-SI-Implicature} $\implicates$ Hans solved
        some but not all of the problems.
      \ex \label{bsp:Plain-SI-Alternative} Hans solved all of the problems.
    \end{xlist}
\end{exe}

\noindent The classical explanation of this inference, following the
pioneering work of \citet{Grice1975:Logic-and-Conve} \citep[see][for
recent overview]{Geurts2010:Quantity-Implic}, is that
(\ref{bsp:Plain-SI-Implicature}) is a pragmatic inference, a so-called
\emph{quantity implicature}, derived by an abductive inference as the
best explanation of why an informed, knowledgable and cooperative
speakers have uttered (\ref{bsp:Plain-SI-Target}) when they could also
have uttered the semantically stronger and relevant
(\ref{bsp:Plain-SI-Alternative}).

% If this upper-bounding inference would occur often and
% systematically enough, then it may well be that also embedded
% occurrences of \emph{some} get enriched, in some fashion or other, to
% contribute the enriched meaning \emph{some but not all} also under the
% scope of other logical operators.
% Indeed, even
% \citeauthor{Grice1975:Logic-and-Conve} envisaged this possibility when
% he wrote: ``It may not be impossible for what starts life, so to
% speak, as a conversational implicature to become conventionalized''
% \citep[p.58]{Grice1975:Logic-and-Conve}.

This paper deals with the interpretation of two types of sentences,
where the scalar item \emph{some} occurs in the scope of other logical
operators. In \as-sentences (short for \textsc{All-Some}) as in (\ref{bsp:AE})
the scalar item \emph{some} is embedded under universal quantifier
\emph{all}. In \es-sentences (short for \textsc{ExactlyOne-Some}) like (\ref{bsp:GE}) \emph{some} takes
scope under the non-monotonic quantifier \emph{exactly
  one}.\dn{explain what non-monotonic means?  here or later?}
According to current pragmatic theory, there are at least three
relevant candidate readings for \as- and \es-sentences: (i) a
\emph{literal reading} like in (\ref{bsp:AE-Literal}) and
(\ref{bsp:GE-Literal}) where \emph{some} has only its literal meaning;
(ii) a \emph{global reading} like in (\ref{bsp:AE-Global}) and
(\ref{bsp:GE-Global}) where, according to Gricean intuition, we enrich
utterances of (\ref{bsp:AE}) and (\ref{bsp:GE}) with the negation of
alternative utterances of the corresponding sentences
(\ref{bsp:AE-Alternative}) and (\ref{bsp:GE-Alternative}) where
\emph{some} is replaced by \emph{all}; and also (iii) a \emph{local
  reading} like in (\ref{bsp:AE-Local}) and (\ref{bsp:GE-Local}) where
\emph{some} is interpreted as \emph{some but not all} in the scope of
the embedding quantifier.

\begin{exe}
  \ex \label{bsp:AE} \mymark{All} of the students read {\mymark{some}} of the
  papers. \hfill{(\as)}

  \begin{xlist}
  \ex \label{bsp:AE-Literal} \mymark{All} of the students read
    {\mymark{some and maybe all}} of the papers. \hfill (\as-\lit)
  \ex \label{bsp:AE-Global}
    \mymark{All} of the students read \mymark{some and maybe all} 
    and  \hfill (\as-\glb)\\
    it's not the case that \mymark{all} of the students read \mymark{all} of the papers.
  \ex \label{bsp:AE-Local}
    \mymark{All} of the students read {\mymark{some  but not all}} of the
    papers. \hfill (\as-\loc)
  \end{xlist}
\end{exe}

\begin{exe}
\ex  \label{bsp:GE} \mymark{Exactly one} of the students read {\mymark{some}} of the
  papers. \hfill{(\es)}

  \begin{xlist}
  \ex \label{bsp:GE-Literal} \mymark{Exactly one} of the students read
    {\mymark{some and maybe all}} of the papers. \hfill (\es-\lit)
  \ex \label{bsp:GE-Global}
    \mymark{Exactly one} of the students read \mymark{some and maybe all} 
    and  \hfill (\es-\glb)\\
    it's not the case that \mymark{exactly one} of the students read \mymark{all} of the papers.
  \ex \label{bsp:GE-Local}
    \mymark{Exactly one} of the students read {\mymark{some  but not all}} of the
    papers. \hfill (\es-\loc)
  \end{xlist}
\end{exe}

\begin{exe}
\ex \label{bsp:AE-Alternative} \mymark{All} of the students read
  {\mymark{all}} of the papers.

\ex \label{bsp:GE-Alternative} \mymark{Exactly one} of the students
  read {\mymark{all}} of the papers.
\end{exe}

% Section~\ref{sec:get-know-your} will discuss these readings
% in more detail, showing that all three readings of each sentence are
% distinct but logically dependent on each other in interesting ways.

\noindent Given this relative abundance of theoretically conceivable
readings, two interlocked empirical questions arise:
\begin{enumerate}[Q1:]
\item which of these three
conceivable readings are available to na\"{i}ve subjects; and
\item which of the available readings are preferred.\fn{It may
    ultimately be impossible to keep unavailability and strong
    dispreference strictly apart. For our purposes this is not
    important. Every time we speak of availability, the so-inclined
    reader may think of non-negligible preference.}
\end{enumerate}
Addressing these questions empirically is relevant because they lie at
the heart of the current debate about the exact location and nature of
the interface between semantics and pragmatics. The controversy
concerns the question to what extent the upper-bounding inference from
\emph{some} to \emph{some but not all} is conventionalized within the
compositional computation of semantic values. For that matter, it is
particularly relevant to assess the availability and relative
preference of local readings. (Section~\ref{sec:theories-predictions}
will discuss the relevant theoretical positions and the significance
of alleged local readings in more detail.)

% Firstly, there are \mymark{pragmatic traditionalists} who seek to
% conserve the spirit of \citeauthor{Grice1975:Logic-and-Conve}'s
% (\citeyear{Grice1975:Logic-and-Conve}) original ideas as much as
% possible
% \citep[e.g.][]{Spector2006:Scalar-Implicat,Sauerland2004:Scalar-Implicat,Russell2006:Against-Grammat,vanRooijSchulz:ExhaustiveInterpretation,Geurts2010:Quantity-Implic,Franke2011:Quantity-Implic}. Traditionalists
% acknowledge the existence of global readings, but might consider local
% readings either unavailable or a beast distinct from scalar
% implicatures. An often phrased intuition of the traditionalists is
% that local readings, since they are special kinds of inferences,
% require special intonation, in particular emphatic stress on the
% scalar item.\dn{give references}

% Opposed to that is the camp of \mymark{lexical conventionalists}
% \citep[e.g.][]{LevinsonPresumptiveMeanings2000,Chierchia:2004_ScalarImplicatures}
% who maintain that scalar \emph{some} is lexically ambiguous between
% the standard logical meaning \emph{some and maybe all} and the
% upper-bounded meaning \emph{some but not all}. As the latter is
% considered a default, lexical conventionalism has no problem
% accounting for local readings, and in fact would consider these the
% preferred readings.

% Thirdly and finally, there is the camp of \mymark{grammaticalists} who
% defend that the distribution of upper-bounded readings of \emph{some}
% is best explained by postulating a silent operator, akin to the
% meaning of the particle \emph{only}
% \citep{Chierchia2006:Broaden-Your-Vi,Fox2007:Free-Choice-and,Magri2011:Another-Argumen,Sauerland2012:The-Computation,ChierchiaFox2008:The-Grammatical,Chierchia2012:FC-Nominals-and}. According
% to the grammatical view, this silent operator may be applied in
% compositional semantics also in the scope of other logical operators,
% but, so as not to overgenerate readings, the availability of readings
% is constraint by the \emph{strongest meaning hypothesis}
% \citep{DalrympleKanazawa1998:Reciprocal-Expr}. Grammaticalist theories
% predict that all three types of readings are available. Moreover,
% according to the grammatical view, the local reading is preferred for
% \as-sentences, while the global one is preferred for
% \es-sentences. (More precisely, as we will see
% Section~\ref{sec:theories-predictions}, depending on the variant of
% the strongest meaning hypothesis employed, either the global reading
% is predicted to be preferred for \es-sentences, or the global and the
% local reading are predicted to be equally preferred.)

A number of empirical studies have already examined the availability
of readings for \as- and \es-sentences
\citep[e.g.][]{GeurtsPouscoulous2009:Embedded-Implic,CliftonDube2010:Embedded-Implic,ChemlaSpector2010:Experimental-Ev}. However,
results have not been as clear-cut as one might have hoped for: for
instance, the available empirical evidence is inconclusive as to
whether local readings exist \citep[see also][for related
discussion]{Tielvan-Tiel2012:Embedded-Scalar} and do not clearly
address all preference relations between readings relevant to
distinguish between theoretical positions. In the following we will
argue that these heterogeneous results are partly due to the specific
tasks used in previous studies, i.e., complexity differences in
variants of the picture-verification paradigm.
% We hypothesized that previous studies might be
% insufficiently informative because of the focus on (variants of) a
% picture-verification paradigm.\dn{relate to Bob van Tiel's work} The
% problem is that in order to test the availability of different
% candidate meanings different pictures have to be presented, so that
% effects of pictorial complexity or stereotypicality could never be
% ruled out entirely.
Moreover, previous studies have only accumulated limited evidence
pertaining to the second question that may help decide between
theoretical positions, namely which of the attested readings subjects
prefer. Finally, previous studies presented target sentences
visually. But as it is often argued that intonational stress on an
embedded scalar item can favor a local reading
\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,ChemlaSpector2010:Experimental-Ev,Geurts2010:Quantity-Implic,Tielvan-Tiel2012:Embedded-Scalar},
it seems important to present target sentences auditorily, so as to be
able to control for effects of ``silent intonation'' that subjects may
apply when reading a sentence (see Bader 1998, Fodor 2000)\dn{provide
  references}.

In reaction to this situation, we therefore presented sentence
material auditorily and also employed a different kind of visual
presentation of the pictorial material: subjects were presented with
pictures that were initially covered and could incrementally be
uncovered at the subjects' request; at each step of uncovering,
subjects had to decide whether they could already give a truth-value
judgement or needed more information (Comry ????)\dn{insert
  references}. This way we obtained behavioral data that is both
indicative of the reading subjects assumed and independent of the
complexity of the visual stimulus. At the same time, we hypothesized
that the incremental nature of this task would shed light on the
preferences over readings, because the temporal distribution of
truth-value judgments would give away which reading subjects were
waiting to evaluate, so to speak. Adding to previous studies, we
therefore made sure that our method is able to reveal information
about preferential readings by including ambiguous test items like
(\ref{bsp:target-related-filler}) which are known to preferentially
receive the late-closure reading in
(\ref{bsp:target-related-filler-LC}) and not the dispreferred, but
attested early-closure reading (\ref{bsp:target-related-filler-EC})
(Frazier 1987 XYZ).\dn{insert proper references}
\begin{exe}
\ex \label{bsp:target-related-filler} The letter is connected with circles and squares with
  suns.
  \begin{xlist}
  \ex \label{bsp:target-related-filler-LC} The letter is connected
    with squares with suns and circles. \hfill (\LC)
  \ex \label{bsp:target-related-filler-EC} The letter is connected
    with circles with suns and squares with suns. \hfill (\EC)
  \end{xlist}
\end{exe}

% \begin{itemize}
% \item Fabian wants to skip the following; Petra wants to enlarge on
%   it; I give first my version, then Petra's
%   \begin{itemize}
%   \item To test whether our method is indeed suitable to detect
%     interpretation preferences, we included ambiguous test items like
%     (\ref{bsp:target-related-filler}) which are known to
%     preferentially receive the late-closure reading in
%     (\ref{bsp:target-related-filler-LC}) and not the dispreferred, but
%     attested early-closure reading
%     (\ref{bsp:target-related-filler-EC}).\dn{insert references to
%       literature on EC-LC processing}

%     \begin{exe}
%     \ex \label{bsp:target-related-filler} The letter is connected with circles and squares with
%       suns.
%       \begin{xlist}
%       \ex \label{bsp:target-related-filler-LC} The letter is connected
%         with squares with suns and circles. \hfill (\LC)
%       \ex \label{bsp:target-related-filler-EC} The letter is connected
%         with circles with suns and squares with suns. \hfill (\EC)
%       \end{xlist}
%     \end{exe}
%   \item To test whether our method is indeed suitable to detect
%     interpretation preferences, we included ambiguous test items like
%     (\ref{bsp:target-related-filler}) which have been repeatedly shown
%     to exhibit preferences in previous studies. We thus included
%     so-called \emph{late-closure structures} in which a propositional
%     phrase can be either attached to the immediately preceding
%     \acro{np} (the ``late-closure'' (\LC) reading as
%     (\ref{bsp:target-related-filler-LC})), or to an
%     \acro{np}-coordination (the ``early-closure'' (\EC) readins as in
%     (\ref{bsp:target-related-filler-EC})). According to principles of
%     structural simplicity, an advantage for the \LC-reading has been
%     repeatedly demonstrated (Frazier 1987 XYZ).\dn{insert proper
%       references}
%     \begin{exe}
%     \ex \label{bsp:target-related-filler} The letter is connected with circles and squares with
%       suns.
%       \begin{xlist}
%       \ex \label{bsp:target-related-filler-LC} The letter is connected
%         with squares with suns and circles. \hfill (\LC)
%       \ex \label{bsp:target-related-filler-EC} The letter is connected
%         with circles with suns and squares with suns. \hfill (\EC)
%       \end{xlist}
%     \end{exe}
%     By including these structures, we intended to control whether
%     dispreferred readings in general were still available to our
%     participants in the specific task used.

% \end{itemize}
% \end{itemize}

% To test whether our method is indeed suitable to detect interpretation
% preferences, we included ambiguous test items like
% (\ref{bsp:target-related-filler}) which have been repeatedly shown to
% exhibit preferences in previous studies.
% \begin{exe}
% \ex \label{bsp:target-related-filler} The letter is connected with circles and squares with
%   suns.
%   \begin{xlist}
%   \ex \label{bsp:target-related-filler-LC} The letter is connected
%     with squares with suns and circles. \hfill (\LC)
%   \ex \label{bsp:target-related-filler-EC} The letter is connected
%     with circles with suns and squares with suns. \hfill (\EC)
%   \end{xlist}
% \end{exe}
% Sentence (\ref{bsp:target-related-filler}) is an example of a
% so-called \emph{late-closure structure} in which a propositional
% phrase can be either attached to the immediately preceding \acro{np}
% (the ``late-closure'' (\LC) reading as
% (\ref{bsp:target-related-filler-LC})), or to an \acro{np}-coordination
% (the ``early-closure'' (\EC) readins as in
% (\ref{bsp:target-related-filler-EC})). According to principles of
% structural simplicity, an advantage for the \LC-reading has been
% repeatedly demonstrated (Frazier 1987 XYZ).\dn{insert proper
%   references}

\medskip

\begin{itemize}
\item summarize results
\end{itemize}

The paper is structured as follows. Section~\ref{sec:get-know-your}
elaborates on the three kinds of relevant readings for our target
sentences. Section~\ref{sec:theories-predictions} works out the
different theoretical positions and their predictions about
availability and preference. Section~\ref{sec:previous-studies} recaps
the results of previous studies on this subject, arguing for the need
of a more refined methodology. Section~\ref{sec:design} describes our
experimental design. Section~\ref{sec:results} states our results,
which we discuss in Section~\ref{sec:discussion}.\dn{rephrase
  eventually}

Three readings are \emph{prima facie} conceivable for the \as- and
\es-sentences in (\ref{bsp:AE}) and (\ref{bsp:GE}). These are
logically dependent in intricate ways.

\paragraph{\as-sentences.}

An \as-sentence like (\ref{bsp:AE}), repeated below, has a literal
reading (\lit) as in (\ref{bsp:AE-Literal}), a global reading (\glb) as in
(\ref{bsp:AE-Global}) and a local reading (\loc) as in (\ref{bsp:AE-Local}).

\begin{exer}{bsp:AE}

@@

  \begin{xlist}
  \ex \mymark{All} of the students read
    {\mymark{some and maybe all}} of the papers. \hfill (\as-\lit)
  \ex
    \mymark{All} of the students read \mymark{some and maybe all} 
    and  \hfill (\as-\glb)\\
    it's not the case that \mymark{all} of the students read \mymark{all} of the papers.
  \ex
    \mymark{All} of the students read {\mymark{some  but not all}} of the
    papers. \hfill (\as-\loc)
  \end{xlist}
\end{exer}

\noindent These readings stand in a strict entailment relation: the
local reading asymmetrically entails the global reading, which
asymmetrically entails the literal reading:
\begin{exe}
  \ex \label{bsp:Entailments-AS} \loc $\subset$ \glb $\subset$ \lit
\end{exe}
\glb entails \lit because, in general, global readings are defined as
the conjunction of the literal reading and the negated
(relevant/feasible) alternative(s) of the to-be-interpreted
utterance. This entailment is asymmetric, because the information that
not all of the students read all of the papers is not entailed by the
literal reading. To see that \loc $\subset$ \glb, notice that the case
where all of the students read some but not all of the papers is a
special case of the case where all of the students read some (and
maybe all), while not all of the students read all of the papers.

Given these entailment relations, there are four kinds of situations,
the names for which we borrow from
\citet{ChemlaSpector2010:Experimental-Ev}, that we can distinguish
based on different truth values for our candidate readings. These are
given in Table~\ref{fig:situations-AE}.
%
\begin{table}
  \centering
  \subfloat[][\as-sentences]{
  \label{fig:situations-AE}
    \begin{tabular}{lccc}
    \toprule
    situation    & \multicolumn{3}{c}{truth value} 
  \\ 
  \cmidrule(r){2-4}
     & \lit & \glb & \loc \\ \midrule
    false   & 0 & 0 & 0 \\
    literal & 1 & 0 & 0 \\
    weak    & 1 & 1 & 0 \\
    strong  & 1 & 1 & 1 \\ \bottomrule
  \end{tabular}
} \qquad \qquad
  \subfloat[][\es-sentences]{
  \label{fig:situations-GS}
  \begin{tabular}{lccc}
    \toprule
    situation    & \multicolumn{3}{c}{truth value} 
  \\ 
  \cmidrule(r){2-4}
    & \textsc{lit} & \textsc{glb} & \textsc{loc} \\ \midrule
    false   & 0 & 0 & 0 \\
    literal & 1 & 0 & 0 \\
    local   & 0 & 0 & 1 \\
    all     & 1 & 1 & 1 \\ \bottomrule
  \end{tabular}
}
\caption{Possible truth-value distributions for readings of \as- and \es-sentences}
\label{tab:situations}
\end{table}
%
Examples of these kinds of situations are given in
Figure~\ref{fig:AS-distinguishing-pics}, where the dots on the right
of each diagram represent students, the dots on the left represent
papers and an arrow from a student to a paper indicates that the
student read the paper.\dn{improve graphics} Notice that other
arrangements of arrows might equally well serve as examples for the
various situations.

\begin{figure}[]
  \centering

\subfloat[fig:false][false]{
  \label{fig:false-AE}

\begin{tikzpicture}[node distance = 1cm]
        % Nodes

        \node (X-1) {$\Large{\bullet}$};

        \node (X-2) [below of = X-1] {$\Large{\bullet}$};

        \node (X-3) [below of = X-2] {$\Large{\bullet}$};

        \node (Y-1) [right of = X-1, node distance = 2cm]{$\Large{\bullet}$};

        \node (Y-2) [below of = Y-1] {$\Large{\bullet}$};

        \node (Y-3) [below of = Y-2] {$\Large{\bullet}$};

        \node (Y-4) [below of = Y-3] {$\Large{\bullet}$};

        % table added from here

        \node (X-4) [below of = X-3, node distance = 2cm] {};

        \node (table) [right of = X-4] {
          \begin{tabular}{ll}
            \lit & false \\
            \glb & false \\
            \loc & false 
          \end{tabular}};

        % Arrows

        \path [draw=blue,->] (X-1) -> (Y-1);

        \path [draw=blue,->] (X-1) -> (Y-2);

        \path [draw=red,->] (X-3) -> (Y-3);

        \path [draw=red,->] (X-3) -> (Y-4);

      \end{tikzpicture}

}
\subfloat[fig:literal][literal]{
  \label{fig:literal-AE}

  \begin{tikzpicture}[node distance = 1cm]
        % Nodes

        \node (X-1) {$\Large{\bullet}$};

        \node (X-2) [below of = X-1] {$\Large{\bullet}$};

        \node (X-3) [below of = X-2] {$\Large{\bullet}$};

        \node (Y-1) [right of = X-1, node distance = 2cm]{$\Large{\bullet}$};

        \node (Y-2) [below of = Y-1] {$\Large{\bullet}$};

        \node (Y-3) [below of = Y-2] {$\Large{\bullet}$};

        \node (Y-4) [below of = Y-3] {$\Large{\bullet}$};

        % table added from here

        \node (X-4) [below of = X-3, node distance = 2cm] {};

        \node (table) [right of = X-4] {
          \begin{tabular}{ll}
            \lit & true \\
            \glb & false \\
            \loc & false 
          \end{tabular}};

        % Arrows

        \path [draw=blue,->] (X-1) -> (Y-1);

        \path [draw=blue,->] (X-1) -> (Y-2);

        \path [draw=blue,->] (X-1) -> (Y-3);

        \path [draw=blue,->] (X-1) -> (Y-4);

        \path [draw=black,->] (X-2) -> (Y-1);

        \path [draw=black,->] (X-2) -> (Y-2);

        \path [draw=black,->] (X-2) -> (Y-3);

        \path [draw=black,->] (X-2) -> (Y-4);

        \path [draw=red,->] (X-3) -> (Y-1);

        \path [draw=red,->] (X-3) -> (Y-2);

        \path [draw=red,->] (X-3) -> (Y-3);

        \path [draw=red,->] (X-3) -> (Y-4);

      \end{tikzpicture}

}
\subfloat[fig:weak][weak]{
  \label{fig:weak}

\begin{tikzpicture}[node distance = 1cm]
        % Nodes

        \node (X-1) {$\Large{\bullet}$};

        \node (X-2) [below of = X-1] {$\Large{\bullet}$};

        \node (X-3) [below of = X-2] {$\Large{\bullet}$};

        \node (Y-1) [right of = X-1, node distance = 2cm]{$\Large{\bullet}$};

        \node (Y-2) [below of = Y-1] {$\Large{\bullet}$};

        \node (Y-3) [below of = Y-2] {$\Large{\bullet}$};

        \node (Y-4) [below of = Y-3] {$\Large{\bullet}$};

        % table added from here

        \node (X-4) [below of = X-3, node distance = 2cm] {};

        \node (table) [right of = X-4] {
          \begin{tabular}{ll}
            \lit & true \\
            \glb & true \\
            \loc & false 
          \end{tabular}};

        % Arrows

        \path [draw=blue,->] (X-1) -> (Y-1);

        \path [draw=blue,->] (X-1) -> (Y-2);

        \path [draw=black,->] (X-2) -> (Y-1);

        \path [draw=black,->] (X-2) -> (Y-2);

        \path [draw=black,->] (X-2) -> (Y-3);

        \path [draw=black,->] (X-2) -> (Y-4);

        \path [draw=red,->] (X-3) -> (Y-3);

        \path [draw=red,->] (X-3) -> (Y-4);

      \end{tikzpicture}

}
\subfloat[fig:strong][strong]{
  \label{fig:strong}

\begin{tikzpicture}[node distance = 1cm]
        % Nodes

        \node (X-1) {$\Large{\bullet}$};

        \node (X-2) [below of = X-1] {$\Large{\bullet}$};

        \node (X-3) [below of = X-2] {$\Large{\bullet}$};

        \node (Y-1) [right of = X-1, node distance = 2cm]{$\Large{\bullet}$};

        \node (Y-2) [below of = Y-1] {$\Large{\bullet}$};

        \node (Y-3) [below of = Y-2] {$\Large{\bullet}$};

        \node (Y-4) [below of = Y-3] {$\Large{\bullet}$};

        % table added from here

        \node (X-4) [below of = X-3, node distance = 2cm] {};
